Work Fragmentation in Developer Interaction Data

### 2016-02-09 paper_2.tex
RQ2 results with Mylyn

\begin{itemize}
\item \textit{low}: the first group consists of sessions where the proportion of prolonged interruptions is $<$0.30, which includes sessions with proportion equal to zero, that is sessions with only short interruptions. These sessions constitute 0000\% in Mylyn and 20.8\% in UDC, from the total of sessions in both datasets.
\item \textit{medium}: the second group consists of sessions with a proportion between 0.30 and 0.50. These sessions constitute 0000\% in Mylyn and 18.9\% in UDC.
\item \textit{high}: the sessions in this group have a proportion $>$0.50, which are the 0000\% in Mylyn and 60.1\% in UDC.
\end{itemize}

@@

The results with Mylyn show...

The Table \ref{tbl:udc_stats_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity.

@@

\begin{table}
\small
\renewcommand{\arraystretch}{1.3}
\caption{Median for the edits per minute, selections per minute and edit ratio according to the number of interruptions and the proportion of prolonged interruptions in UDC.}
\label{tbl:udc_stats_dur_int}
\centering
\begin{tabular}{|p{3cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
	  \hline 
	  & \multicolumn{4}{c|}{Number of interruptions} \\
	  \hline
	Proportion of long int. & none & [1-3] & [4-6] & $>$6 \\  
	  \hline 
	\multicolumn{5}{c}{\textit{Edits per minute}} \\
		\hline
		low & 3.58 &  2.52 & 1.45 & 1.36 \\
		\hline
		medium & 3.58 & 1.25 & 1.15 &  1.27 \\		
		\hline		
		high  & 3.58 & 1.25 & 1 & 0.95   \\
		\hline
	\multicolumn{5}{c}{\textit{Selections per minute}} \\
	    \hline 
		low &  2.54& 2.15 & 1.6 & 1.44\\
		\hline
		medium & 2.54 & 1.5 & 1.5 & 1.41  \\
		\hline				
		high & 2.54&  1.55  & 1.45 & 1.36  \\
	    \hline
	 \multicolumn{5}{c}{\textit{Edit ratio}} \\
	   \hline 
		low & 0.57 & 0.54 & 0.47  & 0.46 \\
		\hline
		medium & 0.57 & 0.45 & 0.44 & 0.46  \\
		\hline				
		high & 0.57 & 0.46 & 0.42 & 0.44  \\
	   \hline
\end{tabular}
\end{table}

>>>>

\begin{itemize}
\item \textit{low}: the first group consists of sessions where the proportion of prolonged interruptions is $<$0.30, which includes sessions with proportion equal to zero, that is sessions with only short interruptions. These sessions constitute 47.7\% in Mylyn and 20.8\% in UDC, from the total of sessions in both datasets.
\item \textit{medium}: the second group consists of sessions with a proportion between 0.30 and 0.50. These sessions constitute 31.8\% in Mylyn and 18.9\% in UDC.
\item \textit{high}: the sessions in this group have a proportion $>$0.50, which are the 20.5\% in Mylyn and 60.1\% in UDC.
\end{itemize}

@@

The Figure \ref{fig:lines_dur_int} shows the median of the metrics when grouping the sessions by the number of interruptions and the proportion of prolonged interruptions with Mylyn, and the Figure \ref{fig:udc_lines_dur_int} with UDC. In this context, it is better to have a low number of interruptions (group [1-3]) and a low proportion of prolonged interruptions, and the results agree with this statement. For example, when having between 1 to 3 interruptions and a low proportion the metrics show higher values when compared to having $>$ 6 interruptions and a high proportion of prolonged interruptions. Moreover, if we focus on a category we can see a gradual decrease as the number of interruptions increases, which lead us to conclude that the proportion of prolonged interruptions has an effect on the developer productivity.

@@

Comparing the results between the datasets, UDC seems to show a more defined difference between groups. The sessions with a low proportion of prolonged interruption has a greater difference (higher productivity) than sessions with medium proportion. In Mylyn this difference is more subtle but can be identified.

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\minipage{1\textwidth}
		\includegraphics[width=\linewidth,clip=, angle=0]{figures/lines_dur_int}  \\
		\endminipage\hfill
	\end{tabular}
	\caption{Plot showing the median values for the metrics according to the proportion of prolonged interruptions and the number of interruptions in Mylyn. }
	\label{fig:lines_dur_int}
\end{figure}

\begin{figure}[!ht]
	\centering
	\begin{tabular}{c}
		\minipage{1\textwidth}
		\includegraphics[width=\linewidth,clip=, angle=0]{figures/udc_lines_dur_int}  \\
		\endminipage\hfill
	\end{tabular}
	\caption{Plot showing the median values for the metrics according to the proportion of prolonged interruptions and the number of interruptions in UDC. }
	\label{fig:udc_lines_dur_int}
\end{figure}

%\begin{table}
%\small
%\renewcommand{\arraystretch}{1.3}
%\caption{Median for the edits per minute, selections per minute and edit ratio according to the number of interruptions and the proportion of prolonged interruptions in UDC.}
%\label{tbl:udc_stats_dur_int}
%\centering
%\begin{tabular}{|p{3cm}|p{1cm}|p{1cm}|p{1cm}|p{1cm}|}
%	  \hline 
%	  & \multicolumn{4}{c|}{Number of interruptions} \\
%	  \hline
%	Proportion of long int. & none & [1-3] & [4-6] & $>$6 \\  
%	  \hline 
%	\multicolumn{5}{c}{\textit{Edits per minute}} \\
%		\hline
%		low & 3.58 &  2.52 & 1.45 & 1.36 \\
%		\hline
%		medium & 3.58 & 1.25 & 1.15 &  1.27 \\		
%		\hline		
%		high  & 3.58 & 1.25 & 1 & 0.95   \\
%		\hline
%	\multicolumn{5}{c}{\textit{Selections per minute}} \\
%	    \hline 
%		low &  2.54& 2.15 & 1.6 & 1.44\\
%		\hline
%		medium & 2.54 & 1.5 & 1.5 & 1.41  \\
%		\hline				
%		high & 2.54&  1.55  & 1.45 & 1.36  \\
%	    \hline
%	 \multicolumn{5}{c}{\textit{Edit ratio}} \\
%	   \hline 
%		low & 0.57 & 0.54 & 0.47  & 0.46 \\
%		\hline
%		medium & 0.57 & 0.45 & 0.44 & 0.46  \\
%		\hline				
%		high & 0.57 & 0.46 & 0.42 & 0.44  \\
%	   \hline
%\end{tabular}
%\end{table}
